A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-18 appendix.tex
Added mock aLIGO noise description
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@639 ccdd05d5-56c1-461a-bf98-85f6876523b4

>>>>

\section{Filter bank for generating mock Advanced {\sc ligo} strain data}
\label{appendix:mock-data}

The filter bank described below reproduces the ``zero detuning, high power'' Advanced \textsc{ligo} noise model of  \cite{Shoemaker:2009p9770} very faithfully.  Since it is composed of a small number of third order or lower linear filters, a digital implementation of it can produce mock data in realtime with negligibly few floating point operations.

First, generate 5 independent streams of white Gaussian noise, $x_1, \dots, x_5$, sampled at 16384 Hz.  Next, the apply the (\textsc{f}/\textsc{i})\textsc{ir} filters described in equation~(\ref{eq:iirbank}) to generate $y_1, \dots, y_5$ from $x_1, \dots, x_5$ respectively.  Finally, sum and scale all of the $y_1, \dots, y_5$ together to obtain the final output $y$.

The power spectrum of $y$ is the sum of squares of the magnitudes of the transfer functions of all of the filters.  The output of the filter bank is compared with the noise model in Figure~\ref{fig:mock-psd} below.

The mock Advanced \textsc{ligo} noise generator is implemented by the GStreamer element \texttt{lal\_fakeadvligosrc}, which is included with the analysis code.

\begin{eqnarray}
\label{eq:iirbank}
x_i &[n] \sim& \mathcal{N}[0, 1] \quad \forall \, i, n \nonumber\\\noalign{\vskip 2mm}
y_1 &[n] =& \left(4 \times 10^{-28}\right) x_1[n] - y_1[n-1] + 2 \cdot .99995 \cos \left(\frac{2\pi \cdot 9.103}{16384}\right) y_1[n-2] - .99995^2 y_1[n-3] \nonumber\\\noalign{\vskip 2mm}
y_2 &[n] =& \left(1.1 \times 10^{-23}\right) (x_2[n] - x_2[n-1]) \nonumber\\\noalign{\vskip 2mm}
y_3 &[n] =& \left(10^{-27}\right) x_3[n] - y_3[n-1] + 2 \cdot .999 y_3[n-2] - .999^2 y_3[n-3] \nonumber\\\noalign{\vskip 2mm}
y_4 &[n] =& \left(4 \times 10^{-26}\right) x_4[n] - y_4[n-1] + 2 \cdot .87 \cos \left(\frac{2\pi \cdot 50}{16384}\right) y_4[n-2] - .87 ^ 2 y_4[n-3] \nonumber\\\noalign{\vskip 2mm}
y_5 &[n] =& \left(6.5 \times 10^{-24}\right) x_5[n] - y_5[n-1] - 2 \cdot .45 y_5[n-2] - .45 ^ 2 y_5[n-3] \nonumber\\\noalign{\vskip 2mm}
\; y &[n] =& \frac{3\sqrt{16384}}{4} \left(y_1[n] + y_2[n] + y_3[n] + y_4[n] + y_5[n]\right)
\end{eqnarray}

\begin{figure}[h!]
\begin{center}
\includegraphics[scale=0.4]{mock_psd.pdf}
\caption{Power spectrum of 100 s of output from mock data filter bank compared with the ``zero detuning, high power'' Advanced \textsc{ligo} noise model.}
\label{fig:mock-psd}
\end{center}
\end{figure}

Note that the \textsc{cpu} overhead of this procedure will be entirely dominated by drawing the pseudorandom numbers $x_1, \dots, x_5$.

### 2011-02-18 results.tex
Added mock aLIGO noise description
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@639 ccdd05d5-56c1-461a-bf98-85f6876523b4

>>>>

We tested the new detection method with mock Advanced \textsc{ligo} data having a power spectrum prescribed by the ``zero detuning, high power'' noise model in \cite{Shoemaker:2009p9770}.  Colored Gaussian noise is generated by passing 5 independent realizations of white Gaussian noise sampled at 16384 Hz through a bank of 5 third-order \textsc{iir} filters, then summing the filters' outputs.  This carefully designed filter bank reproduces the noise model very faithfully, but since it is composed of \textsc{iir} filters it can produce mock data in realtime very cheaply.  See \ref{appendix:mock-data} for implementation details.
